I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-20 Paper/Paper_noProof.tex
conclusion

In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs. We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even very simple Box abstraction (interval arithmetic) suffices to verify accurately DNNs. We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, indeed exhibits paths with larger compensating strength.

>>>>

In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs. We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs. We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.
